---
title: "Reproducible Research: Peer Assessment 1"
autor: "Brenda Rodriguez"
output: html_document
---

## Loading and preprocessing the data

mydata = read.csv("activity.csv", header= TRUE)

## What is mean total number of steps taken per day?

steps_day <- tapply(mydata$steps, mydata$date, sum, na.rm=TRUE)

Histogram of the total number of steps taken each day
```{r, echo=TRUE}
steps_day <- tapply(mydata$steps, mydata$date, sum, na.rm=TRUE)
hist(steps_day, main= "The total number of steps taken each day", xlab = "Steps")
```

Mean and median number of steps taken each day
```{r, echo=TRUE}
mean(steps_day)
median(steps_day)
```

## What is the average daily activity pattern?

Time series plot of the average number of steps taken
```{r, echo=TRUE}
steps_day_mean <- tapply(mydata$steps, mydata$date, mean, na.rm= TRUE)
ts_steps <- ts(steps_day_mean)
plot(ts_steps[!is.na(ts_steps)], type = "l", main= "The average number of steps taken", xlab= "days", ylab= "average")
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}
interval_5_minute <- which.max(tapply(mydata$steps, mydata$interval, mean, na.rm= TRUE))
names(interval_5_minute)
```

## Imputing missing values

Code to describe and show a strategy for imputing missing data
```{r, echo=TRUE}
index_missing<- which(is.na(mydata))
length(index_missing)
```


## Are there differences in activity patterns between weekdays and weekends?
